# Doing it with OSX

## Having fun --- or Not

OK....does **bash** work with OSX?

First, check if the following works at the **R** prompt.

```{r comment = NA}
Sys.which('bash')
```

Cool!  It looks like I am good to go.

Now we will print the working directory from **bash**.

```{r engine = 'bash', comment = NA}
pwd
```

To see if **sh** will work, test to see if it is found on your system.  
I have **xcode** installed on my system.  You may want to install [xcode](https://developer.apple.com/xcode/) if you have not already.

```{r comment = NA}
Sys.which('sh')
```

Hot dog!  This is working.  Issue some commands to see what is in the working directory.

```{r engine = 'sh', comment = NA}
ls -a
```

Maybe a little more information. Note: `-al` lists details for hidden and 
unhiddn files and folders.

```{r engine = 'sh', comment = NA}
ls -al
```
`touch` creates an empty file

```{r engine = 'sh', comment = NA}
touch NewFile
ls
```
```{r engine = 'sh', comment = NA}
rm NewFile
ls
```

What time is it?

```{r engine = 'bash', comment = NA}
date
```

```{r FOLDED, fig.width=4, fig.height =4,fig.align='center'}
#### Folded chunk ####
junk <- rnorm(1000, 100, 10)
hist(junk, col = "red")
library(ggplot2)
ggplot(data.frame(x = junk), aes(x = x)) + geom_histogram()
```