# Doing it with Windows

## Having fun --- or Not

OK....does **bash** work with windows?

First, check if the following works at the **R** prompt.

```{r comment = NA}
Sys.which('bash')
```

Cool!  It looks like I am good to go.

Now we will print the working directory from **bash**.

```{r engine = 'bash', comment = NA}
pwd
```

To see if **sh** will work, test to see if it is found on your system.  
I have **Rtools** installed on my system.  You may want to install [Rtools](http://cran.r-project.org/bin/windows/Rtools/) if you have not already.

```{r comment = NA}
Sys.which('sh')
```

Hot dog!  This is working.  Issue some commands to see what is in the working directory.

```{r engine = 'sh', comment = NA}
ls -a
```

Maybe a little more information. Note: `-al` lists details for hidden and 
unhiddn files and folders.

```{r engine = 'sh', comment = NA}
ls -al
```
`touch` creates an empty file

```{r engine = 'sh', comment = NA}
touch NewFile
ls
```
```{r engine = 'sh', comment = NA}
rm NewFile
ls
```

What time is it?

```{r engine = 'bash', comment = NA}
date
```

```{r graph, comment= NA}
x<- rexp(1000)
hist(x, col="blue")
```

```{r grap, fig.align='center'}
m <- rnorm(2000)
hist(m, col="purple")
```

```{r gra, fig.align='center'}
n <- rbinom(2000)
hist(n, col="salmon")
```

